### 2015-11-03 PrincipiaMetaphysicaAutomationPart1/doc/document/TheoryOfAbstractObjectsV1.tex
some further tests

\ dE{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}e{\isachardoublequoteclose}\ dIO{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io{\isachardoublequoteclose}\ dEIO{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}e{\isasymRightarrow}io{\isachardoublequoteclose}\ dEEIO{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}e{\isacharequal}{\isachargreater}e{\isasymRightarrow}io{\isachardoublequoteclose}\ dEEEIO{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}e{\isacharequal}{\isachargreater}e{\isacharequal}{\isachargreater}e{\isasymRightarrow}io{\isachardoublequoteclose}\ dA{\isacharcolon}{\isacharcolon}{\isacharprime}a\isanewline

@@

\ satifiable\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}io\ opt{\isasymRightarrow}bool{\isachardoublequoteclose}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}{\isacharbrackright}\isactrlsup s\isactrlsup a\isactrlsup t\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline

@@

\ z{\isacharunderscore}box{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymbox}\isactrlsup r\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline

@@

\ z{\isacharunderscore}dia{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymdiamond}\isactrlsup r\ {\isasymphi}\ {\isasymequiv}\ {\isasymnot}\isactrlsup z\ {\isasymbox}\isactrlsup r\ {\isacharparenleft}{\isasymnot}\isactrlsup z\ {\isasymphi}{\isacharparenright}{\isachardoublequoteclose}%

@@

@@

\ z{\isacharunderscore}ordinary{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}O\isactrlsup {\isacharbang}\ {\isasymequiv}\ {\isasymlambda}\isactrlsup {\isadigit{1}}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isasymdiamond}\isactrlsup r\ {\isacharless}{\isachardot}E{\isachardot}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}{\isacharparenright}{\isachardoublequoteclose}%

@@

\ z{\isacharunderscore}abstract{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}A\isactrlsup {\isacharbang}\ {\isasymequiv}\ {\isasymlambda}\isactrlsup {\isadigit{1}}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isasymnot}\isactrlsup z\ {\isasymdiamond}\isactrlsup r\ {\isacharless}{\isachardot}E{\isachardot}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}{\isacharparenright}{\isachardoublequoteclose}%

@@

\ \ {\isasymlambda}\isactrlsup {\isadigit{2}}{\isacharparenleft}{\isasymlambda}x\ y{\isachardot}\ {\isacharparenleft}{\isacharparenleft}{\isacharless}O\isactrlsup {\isacharbang}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}\ {\isasymand}\isactrlsup z\ {\isacharless}O\isactrlsup {\isacharbang}{\isasymbullet}{\isachardot}y{\isachardot}{\isachargreater}{\isacharparenright}\ {\isasymand}\isactrlsup z\ {\isasymbox}\isactrlsup r\ {\isacharparenleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}F{\isachardot}\ {\isacharless}{\isachardot}F{\isachardot}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}\ {\isasymequiv}\isactrlsup z\ {\isacharless}{\isachardot}F{\isachardot}{\isasymbullet}{\isachardot}y{\isachardot}{\isachargreater}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline

>>>>

\ dE{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}e{\isachardoublequoteclose}\ dIO{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io{\isachardoublequoteclose}\ dEIO{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}e{\isasymRightarrow}io{\isachardoublequoteclose}\ dEEIO{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}e{\isasymRightarrow}e{\isasymRightarrow}io{\isachardoublequoteclose}\ dEEEIO{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}e{\isasymRightarrow}e{\isasymRightarrow}e{\isasymRightarrow}io{\isachardoublequoteclose}\ dA{\isacharcolon}{\isacharcolon}{\isacharprime}a\isanewline

@@

\ satisfiable\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}io\ opt{\isasymRightarrow}bool{\isachardoublequoteclose}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}{\isacharbrackright}\isactrlsup s\isactrlsup a\isactrlsup t\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline

@@

\ z{\isacharunderscore}box{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymbox}\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline

@@

\ z{\isacharunderscore}dia{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymdiamond}\ {\isasymphi}\ {\isasymequiv}\ {\isasymnot}\isactrlsup z\ {\isacharparenleft}{\isasymbox}\ {\isacharparenleft}{\isasymnot}\isactrlsup z\ {\isasymphi}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}%

@@

Verifying Modal Logic Principles%
Necessitation holds%
\ necessitation{\isacharunderscore}PropForm{\isacharcolon}\ {\isachardoublequoteopen}{\isasymforall}{\isasymphi}{\isachardot}\ {\isacharbrackleft}{\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharbrackright}\ {\isasymlongrightarrow}\ {\isacharbrackleft}{\isasymbox}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharbrackright}{\isachardoublequoteclose}%
\ necessitation{\isacharunderscore}Form{\isacharcolon}\ \ \ \ \ {\isachardoublequoteopen}{\isasymforall}{\isasymphi}{\isachardot}\ {\isacharbrackleft}{\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharbrackright}\ {\isasymlongrightarrow}\ {\isacharbrackleft}{\isasymbox}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharbrackright}{\isachardoublequoteclose}%
Modal Collapse does not hold%
\ modalCollapse{\isacharunderscore}PropForm{\isacharcolon}\ {\isachardoublequoteopen}{\isasymforall}{\isasymphi}{\isachardot}\ {\isacharbrackleft}{\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymrightarrow}\isactrlsup z\ {\isasymbox}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharbrackright}{\isachardoublequoteclose}%
\ modalCollapse{\isacharunderscore}Form{\isacharcolon}\ \ \ \ \ {\isachardoublequoteopen}{\isasymforall}{\isasymphi}{\isachardot}\ {\isacharbrackleft}{\isacharsemicolon}{\isasymphi}{\isacharsemicolon}\ {\isasymrightarrow}\isactrlsup z\ {\isasymbox}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharbrackright}{\isachardoublequoteclose}%
Verifying S5 Principles%
\ axiom{\isacharunderscore}M{\isacharunderscore}PropForm{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}{\isasymphi}{\isachardot}\ {\isacharparenleft}{\isasymbox}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
\ axiom{\isacharunderscore}M{\isacharunderscore}Form{\isacharcolon}\ \ \ \ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}{\isasymphi}{\isachardot}\ {\isacharparenleft}{\isasymbox}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
\ axiom{\isacharunderscore}B{\isacharunderscore}PropForm{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}{\isasymphi}{\isachardot}\ {\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isasymbox}\ {\isacharparenleft}{\isasymdiamond}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
\ axiom{\isacharunderscore}B{\isacharunderscore}Form{\isacharcolon}\ \ \ \ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}{\isasymphi}{\isachardot}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isasymbox}\ {\isacharparenleft}{\isasymdiamond}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
\ axiom{\isacharunderscore}D{\isacharunderscore}PropForm{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}{\isasymphi}{\isachardot}\ {\isacharparenleft}{\isasymbox}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isasymbox}\ {\isacharparenleft}{\isasymbox}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
\ axiom{\isacharunderscore}D{\isacharunderscore}Form{\isacharcolon}\ \ \ \ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}{\isasymphi}{\isachardot}\ {\isacharparenleft}{\isasymbox}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isasymbox}\ {\isacharparenleft}{\isasymbox}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
\ axiom{\isacharunderscore}{\isadigit{4}}{\isacharunderscore}PropForm{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}{\isasymphi}{\isachardot}\ {\isacharparenleft}{\isasymbox}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isasymdiamond}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
\ axiom{\isacharunderscore}{\isadigit{4}}{\isacharunderscore}Form{\isacharcolon}\ \ \ \ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}{\isasymphi}{\isachardot}\ {\isacharparenleft}{\isasymbox}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isasymdiamond}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
\ axiom{\isacharunderscore}{\isadigit{5}}{\isacharunderscore}PropForm{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}{\isasymphi}{\isachardot}\ {\isacharparenleft}{\isasymdiamond}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isasymbox}\ {\isacharparenleft}{\isasymdiamond}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
\ axiom{\isacharunderscore}{\isadigit{5}}{\isacharunderscore}Form{\isacharcolon}\ \ \ \ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}{\isasymphi}{\isachardot}\ {\isacharparenleft}{\isasymdiamond}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isasymbox}\ {\isacharparenleft}{\isasymdiamond}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
\ test{\isacharunderscore}A{\isacharunderscore}PropForm{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}{\isasymphi}{\isachardot}\ {\isacharparenleft}{\isasymbox}\ {\isacharparenleft}{\isasymdiamond}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isasymdiamond}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
\ test{\isacharunderscore}A{\isacharunderscore}Form{\isacharcolon}\ \ \ \ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}{\isasymphi}{\isachardot}\ {\isacharparenleft}{\isasymbox}\ {\isacharparenleft}{\isasymdiamond}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isasymdiamond}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
\ test{\isacharunderscore}B{\isacharunderscore}PropForm{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}{\isasymphi}{\isachardot}\ {\isacharparenleft}{\isasymdiamond}\ {\isacharparenleft}{\isasymbox}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isasymdiamond}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
\ test{\isacharunderscore}B{\isacharunderscore}Form{\isacharcolon}\ \ \ \ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}{\isasymphi}{\isachardot}\ {\isacharparenleft}{\isasymdiamond}\ {\isacharparenleft}{\isasymbox}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isasymdiamond}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
\ test{\isacharunderscore}C{\isacharunderscore}PropForm{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}{\isasymphi}{\isachardot}\ {\isacharparenleft}{\isasymdiamond}\ {\isacharparenleft}{\isasymbox}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isasymdiamond}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
\ metis%
\ test{\isacharunderscore}C{\isacharunderscore}Form{\isacharcolon}\ \ \ \ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}{\isasymphi}{\isachardot}\ {\isacharparenleft}{\isasymdiamond}\ {\isacharparenleft}{\isasymbox}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isasymdiamond}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
\ metis%
\ test{\isacharunderscore}D{\isacharunderscore}PropForm{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}{\isasymphi}{\isachardot}\ {\isacharparenleft}{\isasymdiamond}\ {\isacharparenleft}{\isasymbox}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isasymbox}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
\ test{\isacharunderscore}D{\isacharunderscore}Form{\isacharcolon}\ \ \ \ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}{\isasymphi}{\isachardot}\ {\isacharparenleft}{\isasymdiamond}\ {\isacharparenleft}{\isasymbox}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isasymbox}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%

@@

\ z{\isacharunderscore}ordinary{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}O\isactrlsup {\isacharbang}\ {\isasymequiv}\ {\isasymlambda}\isactrlsup {\isadigit{1}}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isasymdiamond}\ {\isacharless}{\isachardot}E{\isachardot}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}{\isacharparenright}{\isachardoublequoteclose}%

@@

\ z{\isacharunderscore}abstract{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}A\isactrlsup {\isacharbang}\ {\isasymequiv}\ {\isasymlambda}\isactrlsup {\isadigit{1}}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isasymnot}\isactrlsup z\ {\isacharparenleft}{\isasymdiamond}\ {\isacharless}{\isachardot}E{\isachardot}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}%

@@

\ \ {\isasymlambda}\isactrlsup {\isadigit{2}}{\isacharparenleft}{\isasymlambda}x\ y{\isachardot}\ {\isacharparenleft}{\isacharparenleft}{\isacharless}O\isactrlsup {\isacharbang}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}\ {\isasymand}\isactrlsup z\ {\isacharless}O\isactrlsup {\isacharbang}{\isasymbullet}{\isachardot}y{\isachardot}{\isachargreater}{\isacharparenright}\ {\isasymand}\isactrlsup z\ {\isasymbox}\ {\isacharparenleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}F{\isachardot}\ {\isacharless}{\isachardot}F{\isachardot}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}\ {\isasymequiv}\isactrlsup z\ {\isacharless}{\isachardot}F{\isachardot}{\isasymbullet}{\isachardot}y{\isachardot}{\isachargreater}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
